---
title: "Habitat_Model_Multivariat"
format: html
---

# Clear R environment 
```{r}
#clear R environment -------------------------------------------
rm(list = ls())
```

# Install and load packages 
```{r}
# check for a package, install and load ---------------------------------------
pkgCheck <- function(x){ 
  if (!require(x,character.only = TRUE)){
    install.packages(x,dependencies=TRUE)
    if(!require(x,character.only = TRUE)) {
      stop()
    }
  }
}

pkgCheck("raster")
pkgCheck("spsurvey")
pkgCheck("terra")
pkgCheck("raster")
pkgCheck("ggplot2")
pkgCheck("tibble")
pkgCheck("readr")
pkgCheck("dplyr")
pkgCheck("tidyr")
```


# 1. Input-Data
## a. Water Depth
```{r}
# Read raster-files of water depths -------------------------------------------
depth_path <- "raster_files"

# read raster-files ----------------------------------------------------
depth_2 <- raster(file.path(depth_path, "Landquart_results_depth_2.tif"))


# Set all 0-cells to NA ----------------------------------------------------
depth_2[depth_2 == 0] <- NA
```

## b. Velocity 
```{r}
# Read raster-files of velocities --------------------------------------------
v_path <- "raster_files"

# read raster-files ----------------------------------------------------
velocity_2 <- raster(file.path(v_path, "Landquart_results_velocity_2.tif"))


# Set all 0-cells to NA ---------------------------------------------------
velocity_2[velocity_2 == 0] <- NA
```

## c. Substrate
```{r}
# Read raster-file of substrate --------------------------------------------
sub_path <- "raster_files"

# Read raster-file ----------------------------------------------------
sub <- raster(file.path(sub_path, "Landquart_results_substrate.tif"))

# Set all 0-cells to NA ---------------------------------------------------
velocity_2[velocity_2 == 0] <- NA
```


# 2. Habitat modelling 
## a. Suitability Curves 
```{r}
# Read suitability curves 
### WATER DEPTH ### ----------------------------------------------------
## Tanno 2012 Rhitrhogena sp. ----------------------------------------------------
depth_barbus_path <- "Suitability_Curves_Data/RSE_Gw_HABBY/Barbus_barbus_adult_water_depth.csv" 
depth_barbus <- read.csv(depth_barbus_path, sep=";", dec=".", header = TRUE)

### VELOCITY ### ----------------------------------------------------
# Tanno 2012 Rhithrogena sp. ----------------------------------------------------
v_barbus_path <- "Suitability_Curves_Data/RSE_Gw_HABBY/Barbus_barbus_adult_velocity.csv" 
v_barbus <- read.csv(v_barbus_path, sep=";", dec=".", header = TRUE)
# head(PK_FG)


### SUBTRATE ### ----------------------------------------------------
# Tanno 2012 Baetis sp. ----------------------------------------------------
sub_barbus_path <- "Suitability_Curves_Data/RSE_Gw_HABBY/Barbus_barbus_adult_substrate.csv" 
sub_barbus <- read.csv(sub_barbus_path, sep=";", dec=".", header = TRUE)
```

```{r}
# Plot suitability curves 
### WATER DEPTH ### ----------------------------------------------------
# Tanno 2012 Rhithrogena ----------------------------------------------------
plot(approxfun(depth_barbus$depth, depth_barbus$suitability, method = "linear", rule = 2), xlim = c(0,1.5), 
     main = "HABBY: Barbus barbus", col = "black",  lty = 1, lwd = 2, 
     xlab = "Depth [m]", ylab = "HS [-]")

### VELOCITY ### ----------------------------------------------------
# Tanno 2012 Rhithrogena ----------------------------------------------------
plot(approxfun(v_barbus$velocity, v_barbus$suitability, method = "linear", rule = 2), xlim = c(0,1.5), 
     main = "HABBY: Barbus barbus", col = "black",  lty = 1, lwd = 2, 
     xlab = "Velocity [m/s]", ylab = "HS [-]")

### SUBSTRATE ### ----------------------------------------------------
# Tanno 2012 Baetis ----------------------------------------------------
plot(approxfun(sub_barbus$substrate, sub_barbus$suitability, method = "linear", rule = 2), xlim = c(0,10), 
     main = "HABBY: Barbus barbis", col = "black",  lty = 1, lwd = 2, 
     xlab = "Substrate class", ylab = "HS [-]")
```


## b. Univariate HM 
### b1. water depth
```{r}
### WATER DEPTH ###
# Tanno 2012 Rhithrogena -------------------------------------------
univariat_wd_rhithrogena_tanno_2012 <- function(x, y = sc_depth_Tanno_2012_Rhithrogena$depth..m., z = sc_depth_Tanno_2012_Rhithrogena$Abundance){
  calc(x, fun = approxfun(y, z, rule = 2))
}

# ALL Q's
HS_Tanno_2012_Rhithrogena_depth_2 <- univariat_wd_rhithrogena_tanno_2012(depth_2)


# set coordinate system (crs) -------------------------------------------
crs(HS_Tanno_2012_Rhithrogena_depth_2) <- "+proj=longlat"


# save as .tif -------------------------------------------
# Tanno 2012 Rhithrogena -------------------------------------------
writeRaster(HS_Tanno_2012_Rhithrogena_depth_2, filename="results_univariate/HS_depth_Tanno_2012_Rhithrogena_sp_winter_2.tif", format="GTiff", overwrite=TRUE)
```

### b2. velocity
```{r}
### VELOCITY ###
# Tanno 2012 Rhithrogena -------------------------------------------
univariat_v_rhithrogena_tanno_2012 <- function(x, y = sc_v_Tanno_2012_Rhithrogena$Velocity..m.s., z = sc_v_Tanno_2012_Rhithrogena$Abundance){
  calc(x, fun = approxfun(y, z, rule = 2))
}

# ALL Q's
HS_Tanno_2012_Rhithrogena_velocity_2 <- univariat_v_rhithrogena_tanno_2012(velocity_2)

# Koordinatensystem (crs) -------------------------------------------
crs(HS_Tanno_2012_Rhithrogena_velocity_2) <- "+proj=longlat"


# save as .tif -------------------------------------------
# Tanno 2012: Rhithrogena -------------------------------------------
writeRaster(HS_Tanno_2012_Rhithrogena_velocity_2, filename="results_univariate/HS_velocity_Tanno_2012_Rhithrogena_sp_winter_2.tif", format="GTiff", overwrite=TRUE)
```


### b3. substrate
```{r}
# Substrate (Sub)
# Tanno 2012: Baetis sp. -------------------------------------------
univariat_sub_baetis <- function(x, y = sc_sub_Baetis$Substrate.class, z = sc_sub_Baetis$Abundance){
  calc(x, fun = approxfun(y, z, rule = 2))
}

# All Q's 
HS_sub_Baetis_2 <- univariat_sub_baetis(sub_2)

# Koordinatensystem (crs) -------------------------------------------
crs(HS_sub_Baetis_2) <- "+proj=longlat"


# save as .tif -------------------------------------------
# Tanno 2012: Baetis sp. -------------------------------------------
writeRaster(HS_sub_Baetis_2, filename="results_univariate/HS_sub_Baetis_sp_winter_2.tif", format="GTiff", overwrite=TRUE)
```

## c. GHSI Habitateignungsindex
```{r}
### GHSI ###
# Tanno 2012 Rhithrogena -------------------------------------------
ghsi_3 <- function(x, y, z){
  overlay(x, y, z, 
          sub, fun = return(sqrt(x^3*y^3*z^3)))
}

# All Q's
GHSI_Tanno_2012_Rhithrogena_2 <- ghsi_3(HS_Tanno_2012_Rhithrogena_depth_2, HS_Tanno_2012_Rhithrogena_velocity_2, HS_sub_Rhithrogena_2)


# HABBY Rhithrogena -------------------------------------------
ghsi_2 <- function(x, y){
  overlay(x, y, 
          sub, fun = return(sqrt(x^2*y^2)))
}

# All Q's
GHSI_HABBY_Rhithrogena_2 <- ghsi_2(HS_HABBY_Rhithrogena_depth_2, HS_HABBY_Rhithrogena_velocity_2)


# save as .tif -------------------------------------------
# Tanno 2012: Rhithrogena -------------------------------------------
writeRaster(GHSI_Tanno_2012_Rhithrogena_2, filename="results_multivariate/GHSI_Tanno_2012_Rhithrogena_sp_winter_2.tif", format="GTiff", overwrite=TRUE)
```


### c1. frequency tables
```{r}
# Erstelle Haeufigkeitstabelle 
# Tanno 2012: Rhithrogena -------------------------------------------
freq_table <- function(x){
 as.data.frame(freq(x, digit=1, useNA= "no"))
}

# All Q's
freq_GHSI_Tanno_2012_Rhithrogena_2 <- freq_table(GHSI_Tanno_2012_Rhithrogena_2)
```


## e. Weigthed Usable Area [m2]
```{r}
# define function for WUA calculation -----------------------------------
wua <- function(x){
  cellStats(x, 'sum') * 4
}

# calculate WUA for all Q's -----------------------------------
# Tanno 2012: Rhithrogena -------------------------------------------
WUA_Tanno_2012_Rhithrogena_2 <- wua(GHSI_Tanno_2012_Rhithrogena_2)
```


## f. Wetted Area [m2]
```{r}
# Only for one species, as WA_tot is the same for every species
# define function for WA_tot calculation -----------------------------------
wa_tot <- function(x, column_name){
  sum(x[[column_name]]) * 4
}

# Tanno 2012: Rhithrogena -------------------------------------------
# calculate feq_table for all Q's -----------------------------------
WA_tot_Tanno_2012_Rhithrogena_2 <- wa_tot(freq_GHSI_Tanno_2012_Rhithrogena_2, column_name = "count")
```

## g. Hydraulik Habitat Suitability [-]
```{r}
# Tanno 2012: Rhithrogena -------------------------------------------
# Q2.4
HHS_Tanno_2012_Rhithrogena_2 <- WUA_Tanno_2012_Rhithrogena_2/WA_tot_Tanno_2012_Rhithrogena_2
```

# 4. make dataframe and .csv of calculated indices 
```{r}
# data frame WUA and HHS -------------------------------------------
results <- data.frame(Description = c("Tanno 2012 Baetis sp."), Discharge = c(2.4), 
                      WUA_normal = c(WUA_Tanno_2012_Baetis_2), 
                      WUA_pers_GHSI = c(WUA_pers_Tanno_2012_Baetis_2),
                      WUA_pers_V = c(wua_v_pers_tanno_baetis_2), 
                      HHS = c(HHS_Tanno_2012_Baetis_2),
                      WA_tot = c(WA_tot_Tanno_2012_Rhithrogena_2))

# write data frame into .csv file -------------------------------------------
write.csv(results, file = "results_statistics/Results_Multivariate_Habitat_Model.csv", row.names = FALSE)
```

# 2a. Ver채nderung Habitatverf체gbarkeit in Abh채ngigkeit versch. Abfl체sse 
```{r}
library("readr")
library("tidyr")
library("dplyr")
library("ggplot2")
# make data frame for plotting -------------------------------------------
WUA_HHS <- read_delim("results_statistics/Results_Multivariate_Habitat_Model.csv")

# make variable with WUA normal/persistent -----------------------------------
# long format to plot in facet_wrap 
WUA_normal <- WUA_HHS[ , c(1:3)]
WUA_pers_ghsi <- WUA_HHS[ , c(1,2,4)]
WUA_pers_v <- WUA_HHS[ , c(1,2,5)]

WUA <- full_join(WUA_normal, WUA_pers_ghsi, by = c("Discharge", "Description"))
WUA <- full_join(WUA, WUA_pers_v, by = c("Discharge", "Description"))

WUA_long <- pivot_longer(WUA, cols = c(WUA_normal, WUA_pers_GHSI, WUA_pers_V), names_to = "WUA", values_to = "value")


# Define a custom labelling function
my_labeller <- function(variable, value) {
  if (variable == "WUA") {
    return(c("WUA_normal" = "WUA", "WUA_pers_GHSI" = "WUA persistent GHSI", "WUA_pers_V" = "WUA persistent velocity")[value])
  } 
}

# Plot WUA ALL  -----------------------------------
WUA_results <- ggplot(WUA_long, aes(Discharge, value, col = Description)) +
  facet_wrap(WUA~Description, ncol = 3, nrow = 3, labeller = my_labeller) +
  geom_point(size = 2) +
  geom_line(lwd = 0.7) +
  labs(title = "Comparing Weightes Usable Area (WUA) of three macroinvertebrates", x = expression(paste("Discharge [", m^3/s, "]")), y = "WUA", col = "Macroinvertebrates") +
  theme_gray()

# HHS Plots ALL -----------------------------------
HHS_results <- ggplot(WUA_HHS, aes(Discharge, HHS, col = Description)) +
  facet_wrap(~Description) +
  geom_point(size = 2) +
  geom_line(lwd = 0.7) +
  labs(title = "Comparing Hydraulic Habitat Suitability (HHS) of three macroinvertebrates", x = expression(paste("Discharge [", m^3/s, "]")), y = "HHS [-]", col = "Macroinvertebrates") +
  theme_gray()

# WA tot results -----------------------------------
WA_tot_results <- ggplot(WUA_HHS, aes(Discharge, WA_tot)) +
  geom_line(lwd = 0.7) +
  geom_point(size = 2) +
  labs(title = "Comparing total wetted area of 13 discharges", x = expression(paste("Discharge [", m^3/s, "]")), y = expression(paste("Wettet Area [", m^2, "]"))) +
  theme_gray()
```

```{r}
# save plots into .png
# set the dimensions of the quadrat
quadrat_width <- 30 # in cm
quadrat_height <- 25 # in cm

# WUA 
ggsave(filename = "results_statistics/WUA_results.png",plot = WUA_results, width = quadrat_width, height = quadrat_height, units = "cm")

quadrat_width1 <- 30 # in cm
quadrat_height1 <- 15 # in cm
# HHS
ggsave(filename = "results_statistics/HHS_results.png",plot = HHS_results, width = quadrat_width1, height = quadrat_height1, units = "cm")

# WA_tot
ggsave(filename = "results_statistics/WA_tot_results.png",plot = WA_tot_results, width = quadrat_width, height = quadrat_height, units = "cm")
```






